\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{0.75in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

% --- START OF LATEX MACROS ---
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
% --- END OF LATEX MACROS ---

\begin{document}

\begin{center}
  {\Huge \scshape Phil Maxwell-Mgbudem} \\ \vspace{1pt}
  Ottawa, Canada \enspace • \enspace \href{mailto:maxw0090@algonquinlive.com}{maxw0090@algonquinlive.com} \enspace • \enspace (416) 732-8520 \\
  \href{https://www.linkedin.com/philmaxwell-mgbudem}{linkedin.com/in/philmaxwell-mgbudem} \enspace • \enspace \href{https://github.com/maxphil058}{github.com/maxphil058}
\end{center}

%-----------EDUCATION-----------
\section*{\underline{Education}}
\resumeSubHeadingListStart

  \resumeSubheading
    {Algonquin College}{Jan 2025 -- Present}
    {Diploma in Computer Programming}{Ottawa, Canada}

  \resumeSubheading
    {National Institute of Information Technology (NIIT)}{Jan 2024 -- Aug 2024}
    {Diploma in Full Stack Web Development}{Abuja, Nigeria}

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section*{\underline{Experience}}
\resumeSubHeadingListStart

  \resumeSubheading
    {Freelance Web Developer}{2023 -- Present}
    {Remote}{}
    \resumeItemListStart
      \resumeItem{Developed responsive, full-stack web apps using \textbf{React, Firebase, and SQL}, improving mobile performance scores by 35\%.}
      \resumeItem{Implemented custom automation scripts and back-end logic, streamlining deployment and CI workflows.}
      \resumeItem{Optimized SEO and accessibility across client sites, increasing web traffic by 50\% using Lighthouse metrics.}
    \resumeItemListEnd

  \resumeSubheading
    {Web Developer Intern — E-Clinic \& Diagnostic}{Sep 2024 -- Dec 2024}
    {Lagos, Nigeria}{}
    \resumeItemListStart
      \resumeItem{Collaborated with engineering team to develop modular features for a patient healthcare system using \textbf{JavaScript and PostgreSQL}.}
      \resumeItem{Optimized SQL queries for analytics dashboards, reducing data load time by 40\%.}
      \resumeItem{Participated in Agile ceremonies and performed code reviews, gaining exposure to team-based software development.}
    \resumeItemListEnd

  \resumeSubheading
    {Web Development Assistant — Poshwash DryCleaners}{2022 -- 2023}
    {Abuja, Nigeria}{}
    \resumeItemListStart
      \resumeItem{Contributed to the development of customer service portals using \textbf{React and SQL}, improving engagement by 25\%.}
      \resumeItem{Automated customer record processes with SQL scripts, saving over 10+ hours in weekly manual entry.}
      \resumeItem{Supported system architecture planning and wireframing for feature rollouts in small teams.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section*{\underline{Projects}}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Movie Finder \& Streaming App} • \textit{React, JavaScript, Firebase, REST API}}{2024}
    \resumeItemListStart
      \resumeItem{Built a dynamic UI allowing users to fetch and view real-time movie data from an external REST API.}
      \resumeItem{Integrated Firebase Authentication and Realtime Database for secured user sessions and history tracking.}
      \resumeItem{Linked streaming content through external APIs, enabling seamless viewing experiences.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Task Manager App} • \textit{React, Firebase, Tailwind CSS}}{2024}
    \resumeItemListStart
      \resumeItem{Developed a real-time task tracking system with CRUD functionality using Firebase Cloud Firestore.}
      \resumeItem{Enhanced accessibility and responsiveness through Tailwind CSS, achieving a 95\% Lighthouse score.}
      \resumeItem{Implemented role-based access for multi-user environments, supporting collaborative task delegation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section*{\underline{Technical Skills}}
\resumeSubHeadingListStart
  \resumeSubItem{\textbf{Languages:} Java, JavaScript, Python, C++, C\#, TypeScript}
  \resumeSubItem{\textbf{Web Development:} HTML5, CSS3, React, Tailwind CSS, Bootstrap, Node.js}
  \resumeSubItem{\textbf{Backend \& Databases:} SQL, PostgreSQL, MySQL, Firebase, MongoDB}
  \resumeSubItem{\textbf{Tools \& Frameworks:} Git, GitHub, Docker (basic), VS Code, IntelliJ, Express.js, jQuery}
  \resumeSubItem{\textbf{Concepts:} Object-Oriented Programming, REST APIs, CI/CD, UML, Agile/Scrum, Linux Bash, Testing (JUnit, Postman)}
\resumeSubHeadingListEnd

\end{document}
